### 2023-04-18 main.tex
figure
ii
i

    \includegraphics[scale=0.6]{Dyn_stir.eps}
    \caption{The edge dynamics}

@@

    \includegraphics[scale=0.88]{Dyn_stir_bordo.eps}
    \caption{The site dynamics}

@@

Therefore, we obtain the second cumulant, i.e. the second truncated correlation as 

@@

		\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)

@@

The third cumulant is given by 
	\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]

>>>>

    \includegraphics[scale=0.45]{BulkStirring.eps}
    \caption{The edge dynamics. Maximal occupation is $\nu=6$. A particle of type "square" is removed in $x$ and placed in $y$. A particle of type "triangle" is removed in $y$ and placed in $x$. This transition occurs at rate $n_{square}^{x}n_{triangle}^{y}=2\cdot 3$.}

@@

    \includegraphics[scale=0.4]{BoundaryStirring.eps}
    \caption{The site dynamics. Here the maxiaml occupation is $\nu=6$. The reservoir, represented by a square "box" containing all types of particles, remove a type "square" from site $x$ and replace it with a type "triangle". This transition occurs at rate $\alpha_{triangle}^{x}n_{square}^{y}$.}

@@

Therefore, we obtain the second cumulant, i.e. the two-point connected correlation as 

@@

		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)

@@

Therefore, we obtain the third cumulant, i.e. the three-point connected correlation as 
	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
